---
title: "Tesis"
author: "Vanessa Velázquez Mojica"
date: "31/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(plotly)
library(stringr)
library(plyr)
library(dplyr)
library(class) # KNN
library(ROCR)
library(caret) # ConfusionMatrix
library(knitr) 
library(tidyr) # para manipulacion de datos
library(R.oo)
library(prettydoc)
library(purrr)
library(rpart)
library(randomForest)
library(neuralnet)
library(lubridate)

```

```{r}
# Carga del DataSet
prom_ps <- read_csv("/Users/Vanessa/Desktop/TESIS/Datos/Promedios 24 Hrs/prom_ps.csv")
prom_ps$Date<-as.Date(prom_ps$Date)
names(prom_ps) <- c("date", "id_station", "id_param_ps", "value_ps", "unit_ps")
head(prom_ps)



prom_so2 <- read_csv("/Users/Vanessa/Desktop/TESIS/Datos/Promedios 24 Hrs/Dióxido de Azufre SO2/prome_so2.csv")
prom_so2$Date<-as.Date(prom_so2$Date)
names(prom_so2) <- c("date", "id_station", "id_param_so2", "value_so2", "unit_so2")
head(prom_so2)

prom_24h <- left_join(prom_ps, prom_so2)

prom_24h <- prom_24h[complete.cases(prom_24h), ]

hist(prom_24h$value_ps)
max(prom_24h$value_ps)
table(prom_24h$value_ps)

hist(prom_24h$value_so2)
max(prom_so2$value_so2)
table(prom_24h$value_so2)
```



```{r}

```


### DATA PROFILING

```{r}

#queremos saber que variables son categoricas y cuales numericas
classes <- sapply(prom_ps, function(x) class(x))

categoric_cols <- prom_ps[,which(classes %in% c("character", "factor"))]
numeric_cols <- prom_ps[, -which(classes %in% c("character", "factor"))]

#cuantos valores unicos --cardinalidad
uniques_num <- sapply(numeric_cols, function(x) unique(x) %>% length())
uniques_num <- as.data.frame(uniques_num)

uniques_cat <- sapply(categoric_cols, function(x) unique(x) %>% length())
uniques_cat <- as.data.frame(uniques_cat)

#valores unicos
uniques_values_num <- sapply(numeric_cols, function(x) unique(x))
uniques_values_cat <- sapply(categoric_cols, function(x) unique(x))

#proporcion valores unicos - uniqueness
uniqueness_num <-  round(uniques_num/nrow(prom_ps)* 100, 2)
uniqueness_num <- as.data.frame(uniqueness_num)

uniqueness_cat <-  round(uniques_cat/nrow(prom_ps) * 100, 2)
uniqueness_cat <- as.data.frame(uniqueness_cat)
                                
#checamos si hay vacios 
nan_num <- sapply(numeric_cols, function(x) sum(is.na(x)))
nan_num <- as.data.frame(nan_num)

nan_cat <- sapply(categoric_cols, function(x) sum(is.na(x)))
nan_cat <- as.data.frame(nan_cat)

#para sacar la moda, redondeamos a 2 digitos
my_mode <- function(x, na.rm = T){
  if (class(x) %in% c("character", "factor")) {
    table(x) %>%
      which.max() %>%
      names()
  }
  else {
    table(round(x, 2)) %>%
      which.max() %>%
      names()
  }
}

#moda
modes_num <- sapply(numeric_cols, function(x) my_mode(x, T))
modes_num <- as.data.frame(modes_num)

modes_cat <- sapply(categoric_cols, function(x) my_mode(x, T))
modes_cat <- as.data.frame(modes_cat)

#min 
mins <- sapply(numeric_cols, function(x) min(x, na.rm = T))
mins <- as.data.frame(mins)

#max
maxs <- sapply(numeric_cols, function(x) max(x, na.rm = T))
maxs <- as.data.frame(maxs)

#mean
means <- sapply(numeric_cols, function(x) mean(x, na.rm = T))
means <- as.data.frame(means)

#median
medians <- sapply(numeric_cols, function(x) median(x, na.rm = T))
medians <- as.data.frame(medians)

#1st quantile
first_qtls <- sapply(numeric_cols, function(x) quantile(x,na.rm = T)[2]) #revisa la funcion quantile!
first_qtls <- as.data.frame(first_qtls)

#3rd quantile
third_qtls <- sapply(numeric_cols, function(x) quantile(x, na.rm = T)[4]) 
third_qtls <- as.data.frame(third_qtls)

#sd
sds <- sapply(numeric_cols, function(x) sd(x, na.rm = T))
sds <- as.data.frame(sds)


###generamos nuestra tabla de data profiling
df_categoric <- cbind(uniques_cat, uniqueness_cat, nan_cat, modes_cat)
#no me gusta que tengan en la columna cat... 
names(df_categoric) <- str_replace_all(names(df_categoric), "_cat", "")
names(df_categoric)[2]<-"uniqueness"

df_numeric <- cbind(uniques_num, uniqueness_num, nan_num, mins, maxs, means,
                    sds, medians, modes_num, first_qtls, third_qtls) 
names(df_numeric) <- str_replace_all(names(df_numeric), "_num", "")
names(df_numeric)[2]<-"uniqueness"
```


```{r}
# temp = list.files(pattern = "*.csv")
# myfiles = lapply(temp, read.delim)
# ```

# ```{r}
# promspartsusp <- 
#   rbind.fill(lapply(list.files(path = paste("/Users/Vanessa/Desktop/TESIS/Datos/Promedios 24 Hrs/Particulas Suspendidas PM10 y PM2.5"), "csv"), function(fname)
#     {
#       fpath <- paste(paste("/Users/Vanessa/Desktop/TESIS/Datos/Promedios 24 Hrs/Particulas Suspendidas PM10 y PM2.5"),fname)
#       pps <- read.csv(fpath)
#       pps
#     }
#     ))
```

## R Markdown

<http://rmarkdown.rstudio.com>.
shortcut para chunk: ^OptionI

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
